Interactions in a chemostat as the driver of an ecosystem.

### 2019-12-19 tex/Tracking.tex
changed images and add bib file

Notations used throughout the article are:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
	\item $s$:  vector $(s_1,s_2,s_3)$.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: Dilution Rate of the continuous reactor in $[1/day]$. 
	\item $y_i$: Yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
	\item $y$: vector $y_1,\dots,y_n$.
	\item $k_i$: Yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
	\item $k$: vector $k_1,\dots,k_n$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
\end{enumerate}

@@

\subsection{Reconstructing the Interaction Function}

Suppose that the functions $f_i(s)$, and the yields $y_i$ are well-known. By using experimental measurements of $x$, represented by $z(t)$, the objective is to reconstruct function $I(x)$. For doing so, the terms $I_i(x)$ are replaced by a control $u_i(t)$  and a state feedback is obtained by solving a nonlinear optimal tracking problem.

@@

The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator. $Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear. In the simulations here presented $Q = I_n$ and $R = \lambda I_n$. $\lambda$ is varied from $10^{-1}$ to $10^{-7}$ in the supplementary material section. The case $\lambda = 0.4$ is shown in here for discussion.

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated data as well. 
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
	\caption{Interaction Matrix of the synthetic data.}
	\label{Interaction Matrix Simulation}
\end{figure}

@@

The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}. Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.

@@

@@

For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e. $v(t)= 0$) in  Figure \ref{NoControlSimulation}. $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while.

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Prediction_No_Control_metabolites}
	\caption{Simulation when $u=1$. }
	\label{NoControlSimulation}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_metabolites_Iter_10}
	\caption{Simulation applying the control strategy.}
	\label{ControlSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_AOB_Iter_10}
	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
	\label{AOBSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_NOB_Iter_10}
	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
	\label{NOB Simulation}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_AOB_Iter_10}
	\caption{Control obtained for OTU in $G_1$ (AOB).}
	\label{AOB_control}
	\includegraphics[width= 0.4\textwidth]{Application//191130_Reactor_A_Control_NOB_Iter_10}
	\caption{Control obtained for OTU in $G_2$ (NOB).}
	\label{NOB_control}
\end{figure}

@@

The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the partial conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed. Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability. Furthermore the ecological interpretations to be drawn from the sign of the interaction matrix might be useless. This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.

The interpretation of the correction term as interactions is not the only possible reading. In other contexts the correction term might also be interpreted as a non accounted phenomena ranging from environmental factors (e.g. temperature, pH) to other biological factors (viruses, flock formation, pathogens). Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.

@@

They were solved using standard backward numerical integration.
\section{References}
\bibliographystyle{elsarticle-num}
\bibliography{mybibfile}
\end{document}

>>>>

Notations used throughout the article are:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$.
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$.
	\item $s$:  vector $(s_1,s_2,s_3)$. Refered to as metabolites, or chemical species.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: Dilution Rate of the continuous reactor in $[1/day]$. 
	\item $y_i$: Yield of moles of biomass formed per mole of substrate consumed of OTU $i$.
	\item $y$: vector $y_1,\dots,y_n$.
	\item $k_i$: Yield of  moles of substrate consumed per mole of biomass formed of OTU $i$ . The inverse of the biomass yield $k_i = \dfrac{1}{y_i}$.
	\item $k$: vector $k_1,\dots,k_n$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
\end{enumerate}

@@

\subsection{Unravelling the Interaction Function}

Suppose that the functions $f_i(s)$, and the yields $y_i$ are well-known. By using experimental measurements of $x$, represented by $z(t)$, the objective is to reconstruct function $I(x)$. For doing so, the terms $I_i(x)$ are replaced by controls $u_i(t)$, thus $I_i(x(t)) = u_i(t)$,  and a state feedback is obtained by solving a nonlinear optimal tracking problem.

@@

The choice of matrices $Q$ and $R$ are always of discussion in a quadratic regulator. $Q$ represents the covariance matrix of measurements, while the interpretation of $R$ is not clear. In the simulations here presented $Q = I_n$ and $R = \lambda I_n$. $\lambda$ is varied from $10^{-1}$ to $10^{-7}$ in the supplementary material section. The case $\lambda = 10^{-4}$ is shown in here for discussion.

Figures \ref{Total Biomass no noise}, \ref{AOB no noise}, and \ref{NOB no noise} show the total biomass concentration, and the trajectories for the OTU belonging to $G_1$ and $G_2$, respectively. It can be seen that the method approaches well the trajectories. The metabolites concentration represented in figure \ref{Metabolites no noise} are in accordance with the simulated: The method is able to reconstruct the metabolites trajectories from the community measurements. 
\begin{figure}[h]
	\centering	
	\includegraphics[width=0.5\textwidth]{Synthetic_data_no_noise//Interactions_synthetic_data_no_noise}
	\caption{Interaction Matrix of the synthetic data.}
	\label{Interaction Matrix Simulation}
\end{figure}

@@

The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}. Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1. It should be noted as well that since the synthesized control is not saturated (i.e. it does not reach the imposed bounds) it is optimal.

@@

In figure \ref{Comparison_lambda} the different controls obtained by varying $\lambda$ for two species are compared to the interaction function simulated that is $1+A(x(t))$, where $x(t)$ is the synthetic data. One can see that due to this property of the end value becoming 1, the two do not coincide, however, when $\lambda$ is decreased one can see that the control roughly approaches the respective interaction function at the cost of very sharp changes.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{Synthetic_data//Comparison_different_control}
	\caption{Obtained controled for different $\lambda$ for two OTU and the interaction function used in the simulation of synthetic data.}
	\label{Comparison_lambda}
\end{figure}

@@

For the reader to gain understanding of the situation, a simulation of the system using the experiments operating parameters ($D$ and $s_{in}$) is presented without control (i.e. $u(t)= 1$) in  Figure \ref{u=1_metabolites}. $s_3$ accumulates all along the trajectory, but when compared to data it is clear that $s_3$ stops accumulating after a while. The community dynamics is neither captured by this simulation as seen in figures \ref{u=1_AOB} and \ref{u=1_NOB}.

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_metabolites}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_AOB}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_0}
	\caption{Simulation when $u=1$. }
	\label{u=1_NOB}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_metabolites_Iter_45}
	\caption{Simulation applying the control strategy.}
	\label{ControlSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_AOB_Iter_45}
	\caption{Abundance of $G_1$ (AOB) simulation applying the control strategy.}
	\label{AOBSimulation}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_NOB_Iter_45}
	\caption{Abundance of $G_2$ (NOB) simulation applying the control strategy.}
	\label{NOB Simulation}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_AOB_Iter_45}
	\caption{Control obtained for OTU in $G_1$ (AOB).}
	\label{AOB_control}
	\includegraphics[width= 0.4\textwidth]{Application//191218_Reactor_A_Control_NOB_Iter_45}
	\caption{Control obtained for OTU in $G_2$ (NOB).}
	\label{NOB_control}
\end{figure}

@@

The interaction function introduced tries to address the issue of prediction from the genetic sequencing, leaving the partial conclusion that linear pairwise interaction model do not capture the complexity of the particular nitrifying chemostat analysed. Furthermore from the proof of concept section, one might conjecture that models with a large number of parameters such as an gLV model may be unidentifiable, thus proving to be a real problem in calibration, and therefore of reduced applicability. Furthermore the ecological interpretations to be drawn from the sign of the interaction matrix might be useless. This opens the question for a broader class of interaction functions that could fit well complex microbial ecosystems. The experimental study in chemostat systems seems a good compromise between completely open ecosystems (nature) and controlled conditions (laboratory) in order to explore expressions that could account for microbial interactions.
It is not then possible to reconstruct the original interaction matrix in the current form of the optimal control problem, thus suggesting to take the derivative of the control in the cost function, instead of the control itself.
The interpretation of the correction term as interactions is not the only possible reading. In other contexts the correction term might also be interpreted as a non accounted phenomena ranging from environmental factors (e.g. temperature, pH) to other biological factors (viruses, flock formation, pathogens). Alternative hypothesis for explaining the observed patterns in the microbial community should be considered as well.

@@

They were solved using standard backward numerical integration.

\section{References}
\bibliographystyle{elsarticle-num}
\bibliography{mybibfile}
\end{document}
